---
title: "extracted data summaries"
author: "David Gill"
date: "January 31, 2018"
output: html_document
---
## Functions, packages, and directories
```{r eval=F}
# Clear workspace
rm(list = ls())

# Turn off scientific notation
options(scipen=999,stringsAsFactors = FALSE)

# Packages
library(foreign)
library(readxl)
library(raster)
library(tools)
library(rgeos)
library(rgdal) # readOGR()
library(sp)
library(maptools)
library(prettymapr)
library(RColorBrewer)
library(countrycode) # for assigning ISO codes
library(cowplot)
library(ggplot2)
library(tidyverse)

# Directories
dropbox <- "C:/Users/dgill6/Dropbox/SynergiesTradeoffs.Review/Data extraction/"
datadir <- "C:/Users/dgill6/Dropbox/data/analysis/STEreview/"
# Projections
wgs84 <- CRS("+proj=longlat +ellps=WGS84")
```
### Read in and clean up dataframe
```{r eval=F}
ext.table <- read_excel(paste0(dropbox,'STE extracted results to date.xlsx'), sheet = 1) 
paste0('Are article and outcome exclusion values are identical? ',identical(ext.table$`05 Exclude`,ext.table$`40 Exclude`))
if (!identical(ext.table$`05 Exclude`,ext.table$`40 Exclude`)){
  View(ext.table[ext.table$`05 Exclude`!=ext.table$`40 Exclude`,])
  ext.table <- ext.table[ext.table$`05 Exclude`==ext.table$`40 Exclude`,]
}
# clean up variable names
names(ext.table) <- gsub(" ","_",names(ext.table))
ext.data <- ext.table %>% 
    rename(articleID='Data_extraction_questionnaire.01_Article_ID',
           exclude='05_Exclude',
           pub_typ='11_Publication_type',
           pub_yr='13_Year_of_publication',
           journal='15_Journal', 
           source='110_Source', 
           auth_aff='17_Affiliation_type_of_first_author',           
           int_typ='22_Type_of_intervention',
           int_scale='24_Geographic_scale_of_intervention',           
           int_time='25_Timeframe_of_intervention',           
           int_auth='27_Managing_authority',           
           int_loc='28_Intervention_location',           
           int_area='29_Intevention_area',           
           study_typ='32_Study_type',
           ctrl_gp='33_Study_includes_a_comparison/control_group',
           ctrl_typ='34_Type_of_comparison_(control_group)',
           stdy_source='35_Data_source',           
           stdy_ctry='37_Country_of_study',
           stdy_scl='38_Study_scale',           
           biome='39_Biome', 
           eval_aff='310_Affliation_of_evaluator',           
           stdy_unit='311_Social_unit_of_analysis', 
           stdy_siz='312_Sample_size_(maximum)', 
           stdy_dur='313_Duration_of_study', 
           eqty_dist='51_Distributive_equity', 
           eqty_rcgn='52_Recognitional_equity', 
           eqty_ctxt='53_Contextual_equity', 
           eqty_proc='54_Procedural_equity', 
           cp_toc='61_Causal_pathway/theory_of_change', 
           exp_mech='62_Explicit_mechanism', 
           outcomeID='OutcomeID',
           outcome_stated='41_Stated_outcome_measured',
           outcome_domain='42_Outcome_domain',
           outcome_attr='43_Outcome_attribute',
           outcome_ind='44_Outcome_indicator',
           outcome_obs='45_Perceptions_vs_observed_outcome',
           outcome_data_typ='46_Outcome_data-type',
           resource_typ='47_Resource_use_type',
           outcome_direct='48_Overall_outcome_direction',
           outcome_plrl='49_Pluralism_(who_defines_STEs?)',
           outcome_gp='410_Outcome_sub-group',
           STE_domain='411_STE:_social_domain/HWB_outcomes',
           STE_econgp='412_STE:_(economic_status)',
           STE_socialgp='413_STE:__(social_status)',
           STE_sex='414_STE:__(sex)',
           STE_ethnicgp='415_STE:__(ethnic_group/race)',
           STE_age='416_STE:__(age)',           
           STE_occupation='417_STE:__(occupation)',
           STE_organization='418_STE:_level_of_social_organization',
           STE_spatial_units='419_STE:_spatial_units',
           STE_temporal_units='420_STE:_temporal_units',
           STE_temporal_scale='421_STE:_temporal_scales')

# remove open-ended or unneeded variables
unwanted.var <- grep('(\\d)',names(ext.data),value = T) # variables that still contain a number in the name
ext.data <- ext.data %>% 
  select(-one_of(unwanted.var)) %>%
  mutate(ctrl_typ=gsub("Pre-treatment/post-treatment","Pre/post treatment",ctrl_typ))
  





```

### Basic plot functions
```{r eval=F}
# article level stats
ste_gp <- function (x,y) {
  ext.data %>% 
    filter(exclude=='FALSE') %>% 
    group_by_(x,y) %>% 
    summarise(num=n()) %>%
    arrange(-num) %>%
    ggplot(aes_q(y))+
    geom_bar(stat='count') +
    coord_flip() +
    theme_bw() +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
}
# outcome level stats
ste_gp_o <- function (z) {
 ext.data %>% 
  filter(exclude=='FALSE' & !is.na(z)) %>%
  group_by_(z) %>% 
  summarise(num=n()) %>%
  arrange(-num) }
ste_hist <- function () {
  list(
    geom_histogram(stat='identity'),
    coord_flip(),
    theme_bw(),
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
  )
}

```

### Intervention and study plots
```{r eval=F}
#Percent excluded
length(unique(ext.data$articleID[ext.data$exclude==T]))/length(unique(ext.data$articleID))
pExclude <- ext.data %>% 
    group_by(articleID,exclude) %>% 
    summarise(num=n()) %>% 
  ggplot(aes(exclude)) +
    geom_histogram(stat='count') +
    coord_flip() +
    xlab("Excluded articles") +
    theme_bw() +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

# Publication year
table(ext.data$pub_yr)
minyr <- min(ext.data$pub_yr)-1;maxyr <- max(ext.data$pub_yr)+1
pPubyr<- ext.data %>% 
    filter(exclude=='FALSE') %>% 
    group_by(articleID,pub_yr) %>% 
    summarise() %>% 
    ggplot(aes(pub_yr))+
    geom_histogram(stat='count') +
    scale_x_continuous("Publication year", breaks=seq(minyr,maxyr,5)) +
    theme_bw() +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

# Publication type
pPubtype<-ste_gp(~articleID,~pub_typ) +
  xlab("Publication type")

# Author affliation
table(ext.data$auth_aff)
pAuth_aff<-ste_gp(~articleID,~auth_aff) +
  xlab("Author affliation")

# Intervention type
table(ext.data$int_typ)
pInt_typ<-ste_gp(~articleID,~int_typ) +
  xlab("Intervention type")

# Intervention scale
table(ext.data$int_scale)
pInt_scale<-ste_gp(~articleID,~int_scale) +
  xlab("Intervention scale")

# Type of study
table(ext.data$study_typ)
pStudy_typ<-ste_gp(~articleID,~study_typ) +
  xlab("Study type")

# Study data source
table(ext.data$stdy_source)
pStdy_source<-ste_gp(~articleID,~stdy_source) +
  xlab("Study data source")

# Study scale
table(ext.data$stdy_scl)
pStdy_scl<-ste_gp(~articleID,~stdy_scl) +
  xlab("Study scale")

# Control group
table(ext.data$ctrl_gp)
pCtrl_gp<-ste_gp(~articleID,~ctrl_gp) +
  xlab("Control group")

# Control group type
table(ext.data$ctrl_typ)
pCtrl_typ<-ste_gp(~articleID,~ctrl_typ) +
  xlab("Control group type")

# Biome
table(ext.data$biome)
pBiome<-ste_gp(~articleID,~biome) +
  xlab("Biome")

# Country
table(ext.data$stdy_ctry)
pCountry<-ste_gp(~articleID,~stdy_ctry) +
  xlab("Study country")


# About study
plot_grid(pExclude,pPubyr,pPubtype,pAuth_aff,
          labels=letters[1:4], ncol = 2, nrow = 2, hjust=-1)
ggsave(paste0(datadir,'STE pub info.jpg'),width = 10.5,height = 6)

# About intervention
plot_grid(pInt_typ,pInt_scale,pBiome,pCountry
          ,labels=letters[1:4], ncol = 2, nrow = 2, hjust=-1)
ggsave(paste0(datadir,'STE intervention info.jpg'),width = 14,height = 9)

# About study
plot_grid(pStudy_typ,pStdy_source,pStdy_scl,pCtrl_gp,pCtrl_typ,
          labels=letters[1:5], ncol = 3, nrow = 2, hjust=-1)
ggsave(paste0(datadir,'STE study info.jpg'),width = 10.5,height = 6)

```

### Outcome plots
```{r eval=F}
# Outcome domain
pOut_domain <- ste_gp_o('outcome_domain') %>% 
ggplot(aes(x=reorder(outcome_domain,num),y=num))+
  ste_hist() +
  xlab('Outcome domain')

# Data type
pDatatype <-  ste_gp_o('outcome_data_typ') %>% 
  ggplot(aes(x=reorder(outcome_data_typ,num),y=num))+
  ste_hist() +
  xlab("Outcome data type")
 
# Perceived vs observed
table(ext.data$outcome_obs)
ext.data$outcome_obs1 <- ifelse(ext.data$outcome_obs%in%c('Researcher','Respondent'),
                                ext.data$outcome_obs,"Both")
table(ext.data$outcome_obs1)
pDataobs <- ste_gp_o('outcome_obs1') %>% 
  ggplot(aes(x=reorder(outcome_obs1,num),y=num))+
  ste_hist() +
  xlab("Data 'observer'")

# Dimensions
ste.data <- ext.data %>% 
  filter(exclude=='FALSE') %>% 
  select(STE_domain:STE_temporal_scale)

ste.data1 <-as.data.frame(apply(ste.data, 2, function(x) sum(!is.na(x))))
names(ste.data1)[1] <- "total"
ste.data1$var <- gsub('STE_','',row.names(ste.data1))

pSTE <- ggplot(ste.data1,aes(x=reorder(var,total),y=total)) +
    ste_hist() +
    xlab("STE dimension") 

plot_grid(pDatatype,pDataobs,pOut_domain, pSTE,labels=letters[1:4], 
          ncol = 2, nrow = 2, hjust=-1)
ggsave(paste0(datadir,'STE outcome summaries.jpg'),width = 10.5,height = 6)

```

### Global map
```{r eval=F}
# Add iso3 column to world map for matching to data
world <-  map_data("world") %>% 
  fortify(world,region="group") %>% 
  mutate(iso3=countrycode(region, "country.name", "iso3c"),
       iso3=ifelse(region=='Ascension Island','SHN',iso3),
       iso3=ifelse(region=='Barbuda','ATG',iso3),
       iso3=ifelse(region=='Bonaire','ANT',iso3),
       iso3=ifelse(region=='Canary Islands','ESP',iso3),
       iso3=ifelse(region=='Chagos Archipelago','IOT',iso3),
       iso3=ifelse(region=='Grenadines','VCT',iso3),
       iso3=ifelse(region=='Saba','ANT',iso3),
       iso3=ifelse(region=='Saint Martin','MAF',iso3),
       iso3=ifelse(region=='Sint Eustatius','ANT',iso3),
       iso3=ifelse(region=='Virgin Islands','VGB',iso3))

# Summarise data by country
ctry <- ext.data %>% 
  filter(exclude=='FALSE') %>% 
  group_by(articleID,stdy_ctry) %>% 
  summarise(num=n()) %>% 
  separate(stdy_ctry,c('ctry1','ctry2'),sep=",",remove = F) %>% 
  gather(key=ctry.col,value=ctry,ctry1:ctry2) %>% 
  filter(!is.na(ctry) & !ctry%in%(" United Republic Of")) %>% 
  group_by(ctry) %>% 
  summarise(total=n()) %>% 
  mutate(iso3=countrycode(ctry, "country.name", "iso3c"))

nrow(ctry)

#plot
ste.map <-   world %>% 
  filter(iso3%in%ctry$iso3)
world %>% 
  ggplot(aes(x = long, y = lat, group = group)) +
    geom_polygon(fill='white',col='black') +
    geom_polygon(data=ste.map,fill='blue',col='black')
    
ggsave(paste0(datadir,'STE data map.jpg'),width = 13,height = 7)
```
### Values over time
```{r eval=F}
STE_time <-ext.data %>%
  filter(exclude=='FALSE') %>% 
  select(articleID,pub_yr,STE_domain:STE_temporal_scale) %>%  # replace to your needs
  group_by(articleID,pub_yr) %>% 
  summarise_all(funs(sum(!is.na(.))))  %>% 
  arrange(pub_yr) %>% 
  ungroup() %>% 
  add_count(pub_yr) %>% 
  rename(num.articles=n) %>% 
  mutate_at(vars(STE_domain:STE_temporal_scale),funs(ifelse(.>0,1,0))) %>% 
#  mutate_at(vars(STE_domain:STE_temporal_scale),funs(./num.articles)) %>% 
  group_by(pub_yr,num.articles) %>% 
  summarise_at(vars(STE_domain:STE_temporal_scale),funs(sum)) %>% 
  transmute_at(vars(STE_domain:STE_temporal_scale),funs(./num.articles))
head(STE_time)

pSTE_domain <- ggplot(STE_time,aes(x = pub_yr, y=STE_domain)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('Domain')+ylim(c(0,60))+geom_line(aes(y = cumsum(STE_domain)))
pSTE_econgp <- ggplot(STE_time,aes(x = pub_yr, y=STE_econgp)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('Econ gp')+ylim(c(0,40))+geom_line(aes(y = cumsum(STE_econgp)))
pSTE_socialgp <- ggplot(STE_time,aes(x = pub_yr, y=STE_socialgp)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('socialgp')+ylim(c(0,40))+geom_line(aes(y = cumsum(STE_socialgp)))
pSTE_sex <- ggplot(STE_time,aes(x = pub_yr, y=STE_sex)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('sex')+ylim(c(0,40))+geom_line(aes(y = cumsum(STE_sex)))
pSTE_ethnicgp <- ggplot(STE_time,aes(x = pub_yr, y=STE_ethnicgp)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('ethnicgp')+ylim(c(0,40))+geom_line(aes(y = cumsum(STE_ethnicgp)))
pSTE_age <- ggplot(STE_time,aes(x = pub_yr, y=STE_age)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('age')+ylim(c(0,40))+geom_line(aes(y = cumsum(STE_age)))
pSTE_occupation <- ggplot(STE_time,aes(x = pub_yr, y=STE_occupation)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('occupation')+ylim(c(0,40))+geom_line(aes(y = cumsum(STE_occupation)))
pSTE_organization <- ggplot(STE_time,aes(x = pub_yr, y=STE_organization)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('organizationp')+ylim(c(0,40))+geom_line(aes(y = cumsum(STE_organization)))
pSTE_spatial_units <- ggplot(STE_time,aes(x = pub_yr, y=STE_spatial_units)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('spatial_units')+ylim(c(0,40))+geom_line(aes(y = cumsum(STE_spatial_units)))
pSTE_temporal_units <- ggplot(STE_time,aes(x = pub_yr, y=STE_temporal_units)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('temporal_units')+ylim(c(0,40))+geom_line(aes(y = cumsum(STE_temporal_units)))
pSTE_temporal_scale <- ggplot(STE_time,aes(x = pub_yr, y=STE_temporal_scale)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('temporal_scale')+ylim(c(0,40))+geom_line(aes(y = cumsum(STE_temporal_scale)))

plot_grid(pSTE_domain, pSTE_econgp,pSTE_socialgp,pSTE_sex,
          pSTE_ethnicgp,pSTE_age,pSTE_occupation,pSTE_organization,
          pSTE_spatial_units,pSTE_temporal_units,pSTE_temporal_scale,
          labels=letters[1:12], ncol = 4, nrow = 3, hjust=-1)
ggsave(paste0(datadir,'STE over time.jpg'),width = 13,height = 7)

STE_time_percent <-ext.data %>%
  filter(exclude=='FALSE') %>% 
  select(articleID,pub_yr,STE_domain:STE_temporal_scale) %>%  # replace to your needs
  group_by(articleID,pub_yr) %>% 
  summarise_all(funs(sum(!is.na(.))))  %>% 
  arrange(pub_yr) %>% 
  ungroup() %>% 
  add_count(pub_yr) %>% 
  rename(num.articles=n) %>% 
  mutate_at(vars(STE_domain:STE_temporal_scale),funs(ifelse(.>0,1,0))) %>% 
  group_by(pub_yr,num.articles) %>% 
  summarise_at(vars(STE_domain:STE_temporal_scale),funs(sum)) %>% 
  transmute_at(vars(STE_domain:STE_temporal_scale),funs(./num.articles))
head(STE_time_percent)

pSTE_domain <- ggplot(STE_time_percent,aes(x = pub_yr, y=STE_domain)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('Domain')+ylim(c(0,20))+geom_line(aes(y = cumsum(STE_domain)))
pSTE_econgp <- ggplot(STE_time_percent,aes(x = pub_yr, y=STE_econgp)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('Econ gp')+ylim(c(0,20))+geom_line(aes(y = cumsum(STE_econgp)))
pSTE_socialgp <- ggplot(STE_time_percent,aes(x = pub_yr, y=STE_socialgp)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('socialgp')+ylim(c(0,20))+geom_line(aes(y = cumsum(STE_socialgp)))
pSTE_sex <- ggplot(STE_time_percent,aes(x = pub_yr, y=STE_sex)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('sex')+ylim(c(0,20))+geom_line(aes(y = cumsum(STE_sex)))
pSTE_ethnicgp <- ggplot(STE_time_percent,aes(x = pub_yr, y=STE_ethnicgp)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('ethnicgp')+ylim(c(0,20))+geom_line(aes(y = cumsum(STE_ethnicgp)))
pSTE_age <- ggplot(STE_time_percent,aes(x = pub_yr, y=STE_age)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('age')+ylim(c(0,20))+geom_line(aes(y = cumsum(STE_age)))
pSTE_occupation <- ggplot(STE_time_percent,aes(x = pub_yr, y=STE_occupation)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('occupation')+ylim(c(0,20))+geom_line(aes(y = cumsum(STE_occupation)))
pSTE_organization <- ggplot(STE_time_percent,aes(x = pub_yr, y=STE_organization)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('organizationp')+ylim(c(0,20))+geom_line(aes(y = cumsum(STE_organization)))
pSTE_spatial_units <- ggplot(STE_time_percent,aes(x = pub_yr, y=STE_spatial_units)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('spatial_units')+ylim(c(0,20))+geom_line(aes(y = cumsum(STE_spatial_units)))
pSTE_temporal_units <- ggplot(STE_time_percent,aes(x = pub_yr, y=STE_temporal_units)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('temporal_units')+ylim(c(0,20))+geom_line(aes(y = cumsum(STE_temporal_units)))
pSTE_temporal_scale <- ggplot(STE_time_percent,aes(x = pub_yr, y=STE_temporal_scale)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('temporal_scale')+ylim(c(0,20))+geom_line(aes(y = cumsum(STE_temporal_scale)))

plot_grid(pSTE_domain, pSTE_econgp,pSTE_socialgp,pSTE_sex,
          pSTE_ethnicgp,pSTE_age,pSTE_occupation,pSTE_organization,
          pSTE_spatial_units,pSTE_temporal_units,pSTE_temporal_scale,
          labels=letters[1:12], ncol = 4, nrow = 3, hjust=-1)
ggsave(paste0(datadir,'STE over time_percent.jpg'),width = 13,height = 7)

# By year and intervention
STE_time_int <-ext.data %>%
  filter(exclude=='FALSE') %>% 
  select(articleID,pub_yr,int_typ,STE_domain:STE_temporal_scale) %>%  # replace to your needs
  group_by(articleID,pub_yr,int_typ) %>% 
  summarise_all(funs(sum(!is.na(.))))  %>% 
  arrange(pub_yr) %>% 
  ungroup() %>% 
  add_count(pub_yr,int_typ) %>% 
  rename(num.articles=n) %>% 
  mutate_at(vars(STE_domain:STE_temporal_scale),funs(ifelse(.>0,1,0))) %>% 
#  mutate_at(vars(STE_domain:STE_temporal_scale),funs(./num.articles)) %>% 
  group_by(pub_yr,int_typ,num.articles) %>% 
  summarise_at(vars(STE_domain:STE_temporal_scale),funs(sum)) %>% 
  gather(key=dimension,value=val,STE_domain:STE_temporal_scale) 
#  filter(val>0)
View(STE_time_int)

STE_time_int %>% 
  filter(dimension=='STE_domain' & val>0) %>% pull(pub_yr) 

ggplot(filter(STE_time_int,dimension=='STE_domain'),aes(x = pub_yr, y=val,fill=int_typ,alpha=0.5)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('Domain')+ylim(c(0,20))+geom_area(aes(y = cumsum(val)),position = "identity") 

pSTE_domain <- ggplot(STE_time_int,aes(x = pub_yr, y=STE_domain,fill=int_typ,alpha=0.5)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('Domain')+ylim(c(0,60))+geom_area(aes(y = cumsum(STE_domain)),position = "identity")
pSTE_econgp <- ggplot(STE_time_int,aes(x = pub_yr, y=STE_econgp,fill=int_typ,alpha=0.5)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('Econgp')+ylim(c(0,40))+geom_area(aes(y = cumsum(STE_econgp)),position = "identity")
pSTE_socialgp <- ggplot(STE_time_int,aes(x = pub_yr, y=STE_socialgp,fill=int_typ,alpha=0.5)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('Socialgp')+ylim(c(0,40))+geom_area(aes(y = cumsum(STE_socialgp)),position = "identity")
pSTE_sex <- ggplot(STE_time_int,aes(x = pub_yr, y=STE_sex,fill=int_typ,alpha=0.5)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('sex')+ylim(c(0,40))+geom_area(aes(y = cumsum(STE_sex)),position = "identity")
pSTE_ethnicgp <- ggplot(STE_time_int,aes(x = pub_yr, y=STE_ethnicgp,fill=int_typ,alpha=0.5)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('ethnicgp')+ylim(c(0,40))+geom_area(aes(y = cumsum(STE_ethnicgp)),position = "identity")
pSTE_age <- ggplot(STE_time_int,aes(x = pub_yr, y=STE_age,fill=int_typ,alpha=0.5)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('age')+ylim(c(0,40))+geom_area(aes(y = cumsum(STE_age)),position = "identity")
pSTE_occupation <- ggplot(STE_time_int,aes(x = pub_yr, y=STE_occupation,fill=int_typ,alpha=0.5)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('occupation')+ylim(c(0,40))+geom_area(aes(y = cumsum(STE_occupation)),position = "identity")
pSTE_organization <- ggplot(STE_time_int,aes(x = pub_yr, y=STE_organization,fill=int_typ,alpha=0.5)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('organizationp')+ylim(c(0,40))+geom_area(aes(y = cumsum(STE_organization)),position = "identity")
pSTE_spatial_units <- ggplot(STE_time_int,aes(x = pub_yr, y=STE_spatial_units,fill=int_typ,alpha=0.5)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('spatial_units')+ylim(c(0,40))+geom_area(aes(y = cumsum(STE_spatial_units)),position = "identity")
pSTE_temporal_units <- ggplot(STE_time_int,aes(x = pub_yr, y=STE_temporal_units,fill=int_typ,alpha=0.5)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('temporal_units')+ylim(c(0,40))+geom_area(aes(y = cumsum(STE_temporal_units)),position = "identity")
pSTE_temporal_scale <- ggplot(STE_time_int,aes(x = pub_yr, y=STE_temporal_scale,fill=int_typ,alpha=0.5)) +
    ylab("Frequency") + scale_x_continuous(name="Year", breaks=seq(1990,2015,5)) +
    ggtitle('temporal_scale')+ylim(c(0,40))+geom_area(aes(y = cumsum(STE_temporal_scale)),position = "identity")

plot_grid(pSTE_domain + theme(legend.position="none"), 
          pSTE_econgp + theme(legend.position="none"),
          pSTE_socialgp + theme(legend.position="none"),
          pSTE_sex + theme(legend.position="none"),
          pSTE_ethnicgp + theme(legend.position="none"),
          pSTE_age + theme(legend.position="none"), 
          pSTE_occupation + theme(legend.position="none"),
          pSTE_organization + theme(legend.position="none"),
          pSTE_spatial_units + theme(legend.position="none"),
          pSTE_temporal_units + theme(legend.position="none"),
          pSTE_temporal_scale,
          labels=letters[1:12], ncol = 4, nrow = 3, hjust=-1)
ggsave(paste0(datadir,'STE over time_intervention.jpg'),width = 18,height = 10)


minyr <- min(ext.data$pub_yr)-1;maxyr <- max(ext.data$pub_yr)+1
pInt_time <-ext.data %>% 
  filter(exclude=='FALSE') %>% 
  group_by(articleID,pub_yr,int_typ) %>% 
  summarise(num=n()) %>%
  ungroup() %>% 
  select(pub_yr,int_typ)%>% 
  ggplot(aes(pub_yr)) +
  geom_bar(aes(fill = int_typ)) +
  scale_x_continuous("Publyear", breaks=seq(minyr,maxyr,5)) 

pStudy_typ_time <-ext.data %>% 
  filter(exclude=='FALSE') %>% 
  group_by(articleID,pub_yr,study_typ) %>% 
  summarise(num=n()) %>%
  ungroup() %>% 
  select(pub_yr,study_typ)%>% 
  ggplot(aes(pub_yr)) +
  geom_bar(aes(fill = study_typ)) +
  scale_x_continuous("Publyear", breaks=seq(minyr,maxyr,5)) 

plot_grid(pInt_time+theme(legend.position="right"), pStudy_typ_time+theme(legend.position="right"),
          labels=letters[1:2], ncol = 1, nrow = 2, hjust=-1)
ggsave(paste0(datadir,'study over time.jpg'),width = 10.5,height = 6)


  
```


# Perceived vs observed
 ext.data %>% 
    filter(exclude=='FALSE') %>% 
    group_by(outcome_obs,outcome_domain) %>% 
    summarise(total=n()) %>% 
  ggplot(aes(x=reorder(outcome_domain,total),y=total, fill=outcome_obs)) +
    geom_histogram(stat='identity',position=position_dodge()) +
    coord_flip() +
    theme_bw() +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
